Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-30 paper_comparison/paper_comparison/paper_comparison.Rmd
rearrange the data used in the result

In the following analysis, lineups with uniform fitted values will be the focus of next two sections. Visual patterns are more likely to be revealed under a uniform distribution. Additionally, we have collected extra evaluations on these lineups, which will result in more reliable analysis. Analysis of lineups with other fitted value distributions can be found in Section \ref{fitted-value-distribution}.

@@

## Effect of other factors used in the simulation model

>>>>

In the following analysis, lineups with uniform fitted values will be the focus. Visual patterns are more likely to be revealed under a uniform distribution. Additionally, we have collected extra evaluations on these lineups, which will result in more reliable analysis. Analysis of lineups with other fitted value distributions can be found in Section \ref{effect-of-other-fitted-value-distributions}.

@@

## Effect of other fitted value distributions

### 2023-01-30 paper_comparison/paper_comparison/paper_comparison.tex
rearrange the data used in the result

\hypertarget{effect-of-other-factors-used-in-the-simulation-model}{%
\subsection{Effect of other factors used in the simulation
model}\label{effect-of-other-factors-used-in-the-simulation-model}}

>>>>

\hypertarget{effect-of-other-fitted-value-distributions}{%
\subsection{Effect of other fitted value
distributions}\label{effect-of-other-fitted-value-distributions}}
